---
title: "ps4"
author: "Gustavo Gil"
date: "2/2/2018"
output: html_document
---

CHAPTER 2


```{r}
library(tidyverse)
diamonds
```

1. Carat is the most important variable in prdictig the price of
diamonds. Carat and cut have a positive correlation in some cases and negative in other.

```{r}
regdiamond <- lm(price ~ carat + cut + color + clarity
               + depth + table, data = diamonds)
summary(regdiamond)
```

```{r}
regcarat.cut <- lm(carat ~ cut, data = diamonds)
summary(regcarat.cut)
```

2.

```{r} 
ggplot(data = diamonds) + 
  geom_count(mapping = aes(x = cut, y = color))
```

```{r} 
ggplot(data = diamonds) + 
  geom_count(mapping = aes(x = color, y = cut))
```


3. I think that it is easier to read the table when we use 
aes(x = color, y = cut). When we read a graph like this, we
start from left to right, and having the name of the cut instead 
of only the letter that represents the color, makes it more
intuitive for the user to read the data.

```{r}
ggplot(data = diamonds, 
  mapping = aes(x = price, color = cut_width(carat, 1))) + geom_freqpoly()
```

```{r}
ggplot(data = diamonds, 
  mapping = aes(x = price, color = cut_number(carat, 5))) + geom_freqpoly()
```

4. In cut_width I need to consider the need to make specific analysis
about different segments of the data; on cut_number, I want to know 
what are the most important groups by their number based on the 
recommendation of the software. The first will only be useful if the
groupings have enough observations; thr second will be useful by software
design, but might not be if we want to analyze an specific aspect of
the data without enough observations.

6.The distribution of large diamonds is much more dispersed than small
ones. I believe the reason is that the market of small diamonds must
be indifferent about particular characteristics of the diamond; buyers
are primarily interested in the low cost. Instead, the most the buyers
are willing to pay for diamonds, they will not only be interested
in the carat, but also in the cut, the color, the brand, etcetera.

```{r}
ggplot(data = diamonds, aes(cut_number(price,10), y = carat)) + geom_boxplot()
```


7. 

```{r}
ggplot(diamonds) + geom_point(aes(x = carat, y = price, color = cut))
```

```{r}
ggplot(diamonds) + geom_tile(aes(x = cut, y = carat, fill = price))
```

8. In bins, the graph is much more visible where a high number of
observations overlap. While in a scatterplot, individual observations
are evident just by taking a look at the graph.

```{r}
ggplot(data = diamonds) +
geom_point(mapping = aes(x = x, y = y)) + coord_cartesian(xlim = c(4, 11), ylim = c(4, 11))
```


CHAPTER 10

1. We can know that an object is a tibble because its lists (the columns)
are of the same lenght.

```{r}
mtcars
```

2. Unlike the data frame from the code chunk that gives the observation
of the column "xyz", when calling for printing the "column" x in tibble, results in the  following message "Unknown or uninitialised column: 'x'.NULL". 

```{r}
d_f <- data.frame(abc = 1, xyz = "a")
```

```{r}
d_f$x
```

```{r}
d_f[, "xyz"]
```
```{r}
d_f[, c("abc", "xyz")]
```

```{r}
d.f <- tibble (
abc = 1,
xyz = "a"
)
```

```{r}
d.f$x
```
```{r}
d.f[, "xyz"]
```
```{r}
d.f[, c("abc", "xyz")]
```

3. We can extract the reference variable by using the column number in which
it is located. If its location is the first column, then we can use
names(x)[1]

4. We can convert simple named vectors into tibbles with enframe().
See (https://tjmahr.github.io/tibble-package-tour/=). I migh use it when I want to transfor a particular result from some caculation on a tibble into another tibble.

5. options(tibble.print_max = n, tibble.print_min = m) is the control option for the additional names of columns that are printed, tibble.print_max = n which defines the maximum amount of column names we want to see.

CHAPTER 11

1. I would use read.cvs(data, sep = "|")

2. The most important arguments are the path to the file (file); the column positions (col_positions); specify the type of the column (col_types); the locale default in case the data will be used in a country outside the US; specify the missing values in case of existence. There are other arguments that have to be used in case of special conditions of the data frame imported.

3. In order to read "x,y\n1,'a,b'" in a data frame, we would need to specify the following arguments: the file path; "," as the delim argument; "'"" as the single character that quotes the string; escape_backlash = TRUE.

4. read_csv("a,b,c\n1,2,3\n4,5,6")
read_csv("a,b,c\n1,2,1\n2,3,4")
read_csv("a,b\n1,.", na = ".")
read_csv("a,b\n1,2\.,.", na = ".")
read_csv("a,b\n1,3")

5. date_format and time_format are the default arrangement formats for a country.

